%\newpage

\cvsection{\faBuildingO\space Experience}

\begin{cventries}
  \cventry
    {Postdoctoral Associat} % Job title
    {Handelsman Lab, Wisconsin Institute for Discovery} % Organization
    {Madison, WI} % Location
    {06/2016--present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Genomics and metabolomics of antibiotic discovery through the Tiny Earth initiative.}
      \end{cvitems}
    }
  \cventry
    {Co-Founder, Director of Technology, Senior Consultant} % Job title
    {WiSolve Consulting} % Organization
    {Madison, WI} % Location
    {03/2016--present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided business services (including market research analysis, business plan development, competitive landscape analysis, SBIR grant writing, and others) to early-stage companies in the biotech and pharmaceutical industries.}
      \end{cvitems}
    }
  \vspace{0.4cm}
  \cventry
	{Postdoctoral Associate}
	{Currie Lab, University of Wisconsin-Madison}
	{Madison, WI}
	{04/2019--05/2019}
	{}
  \vspace{-0.4cm}	
  \cventry
    {PhD Candidate} % Job title
    {} % Organization
    {} % Location
    {08/2015--04/2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built genomics-driven computational and analytic pipelines to uncover novel therapeutics and study the evolution of biosynthesis in free-living and host-associated microbes.}
        \item {Systems investigated include insects (leaf-cutting ants, honey bees, \& insects broadly), marine invertebrates, soil communities, \& the human microbiome.}
        \item {Led computational arm of Wisconsin Antimicrobial Drug Discovery \& Development Center (NIH CETR).}
      \end{cvitems}
    }
    
  \cventry
    {Lead Computational Biologist} % Job title
    {Johnson Biosignatures Lab, Harvard \& Georgetown Universities} % Organization
    {Cambridge, MA} % Location
    {10/2013--10/2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Performed whole genome sequencing and metagenomic analysis of environmental samples from sulfur-rich, extreme environments with implications in microbial ecology, biogeochemistry, and exobiology.}
        \item {Characterized biosynthetic potential of metagenomic data.}
      \end{cvitems} 
    }
    
  \cventry
    {Head of Experimental Genomics} % Job title
    {Warp Drive Bio} % Organization
    {Cambridge, MA} % Location
    {04/2013--08/2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Executed genomic-directed natural products drug discovery, high throughput Next Generation Sequencing (htNGS), computational biology, and molecular biology of actinomycetes and fungi.}
        \item {Designed and implemented genomic natural products searches over various scaffolds of business development and internal interest.}
        \item {Developed and curated computational pipelines and databases for assembly, annotation, and custom analysis of public and internal htNGS data (160,000 bacterial genomes, >150 closed and complete genomes) for analysis of novel polyketide, non-ribosomal peptide, and other natural product classes.}
        \item {Handled processing and management of sequence data, predictions, and analyses supporting multiple projects across discovery, molecular biology, engineering, and synthetic biology.}
        \item {Executed elucidation and prediction of novel chemical products of bacterial biosynthetic gene clusters and metabolic pathways (e.g. beta-lactams, aminoglycosides, rapamycin analogues, etc.).}
        \end{cvitems} }
  \cventry
    {}
    {}
    {}
    {}
    { \begin{cvitems}
        \item {Developed internal pipelines for applied phylogenomic annotations and prioritizations of multiple data types to inform discovery and engineering efforts.}
        \item {Oversaw all lab and experimental support of actinomycete and fungal sequencing efforts for Illumina, Pacific Biosciences, and Oxford-Nanopore platforms.}
        \item {Bioinformatics software development to support molecular and synthetic biology efforts.}
        \item {Direct written and verbal communication of findings to senior leadership and business partners.}
        \item {Database management and delivery of sequence information to molecular biology, microbiology, and chemistry groups to aid drug discovery, strain engineering, and generation of expression constructs.}
      \end{cvitems}
    }
  \vspace{0.4cm}
  \cventry
    {Research Assistant, Microbiology \& Computational Biology} % Job title
    {Maira-Litr\'{a}n Infectious Disease Lab, Brigham \& Women's Hospital} % Organization
    {Boston, MA} % Location
    {03/2013--08/2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Investigated \textit{in vivo} fitness, horizontal gene transmission, and pathogenesis of \textit{Acinetobacter baumannii}, \textit{Staphylococcus aureus}, \textit{Salmonella typhii}, and other virulent pathogens through microbiology, computational, and genomic techniques.}
        \item {Developed and optimized genetic tools to enable novel examinations of pathogen fitness, invasion, and virulence using high-throughput transposon-directed insertion site sequencing of infections in murine models.}
      \end{cvitems}
    }
    
  \cventry
    {Research Associate II, Molecular Biology Process Development} % Job title
    {Broad Institute of MIT \& Harvard} % Organization
    {Cambridge, MA} % Location
    {01/2011--03/2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Independently designed development initiatives including supporting htNGS, microfluidics, and automation goals.}
        \item {Oversaw production and up-scaling of microbial mate-pair library construction (LC), integrated internal development with vendor technologies, and managed sample-tracking via real-time messaging to internal LIMS.}
        \item {Increased throughput of microbial LC Platform 4-fold by automation and protocol development.}
        \item{Worked extensively with mate-pair NGS LC, sequence analysis tools, genomic databases, statistical software, and programming/operating lab robotics.}
      \end{cvitems}
    }
    
  \cventry
    {Research Associate, Molecular Genetics} % Job title
    {Rutledge Molecular Genetics Lab, Rensselaer Polytechnic Institute} % Organization
    {Troy, NY} % Location
    {05/2010--12/2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed protocols and operating procedures for transgenic \textit{Caenorhabditis elegans} cultures to model stress-induced neural degeneration and Parkinson's Disease.}
      \end{cvitems}
    }
    
  \cventry
    {Research Assistant, Microbiology} % Job title
    {BCR Biotech} % Organization
    {Jamestown, RI} % Location
    {09/2009--12/2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Wrote and optimized protocols and methods for engineering synthetic biosensing functions in \textit{Bacillus} spores.}
      \end{cvitems}
    }
\end{cventries}
