%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Peer-reviewed Publications}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvpubs}
  \cvpub
    {\hspace{-1cm} *\textit{contributed equally}} % Ref
    {} % Number
  \cvpub
    {\textbf{MG Chevrette}, CM Carlson, HE Ortega, C Thomas, GE Ananiev, KJ Barns, AJ Book, J Cagnazzo, C Carlos, W Flanigan, KJ Grubbs, HA Horn, FM Hoffman, JL Klassen, JJ Knack, GR Lewin, BR McDonald, L Muller, WGP Melo, AA Pinto-Tom\'{a}s, A Schmitz, E Wendt-Pienkowski, S Wildman, M Zhao, F Zhang, J Clardy, TS Bugni, DR Andes, MT Pupo, CR Currie. ``New antibiotics from insect microbiomes." \textit{Under review}.
    } % Ref
    {P9} % Number    
  \cvpub
    {N Liu,* H Li,* \textbf{MG Chevrette}, L Zhang, L Cao, H Zhou, X Zhou, Z Zhou, PB Pope, CR Currie, Y Huang, Q Wang. ``Functional Metagenomics Reveals Polysaccharide-degrading Gene Clusters and Cellobiose Utilization Pathways in Gut Microbiota of a Wood-feeding Termite." \textit{Under review}.
    } % Ref
    {P8} % Number
  \cvpub
    {N Adnani, \textbf{MG Chevrette}, SN Adibhatla, F Zhang, Q Yu, D Braun, J Nelson, SW Simpkins, BR McDonald, CL Myers, J Piotrowski, C Thompson, CR Currie, L Li, SR Rajski, TS Bugni. (2017). ``Co-culture of Marine Invertebrate-Associated Bacteria and Interdisciplinary Technologies Enable Biosynthesis and Discovery of a New Antibiotic, Keyicin." \textit{\textbf{ACS Chemical Biology}}, 12(12), 3093.  https://doi.org/10.1021/acschembio.7b00688 
    } % Ref
    {P7} % Number
  \cvpub
    {AF Sanchez-Larrayoz, NM Elshamy, \textbf{MG Chevrette}, Y Fu, P Giunta, RG Spallanzani, K Ravi, GB Pier, S Lory, T Maira-Litr\'{a}n. (2017). ``Complexity of Complement-Resistance Factors Expressed by \textit{Acinetobacter baumannii} Needed for Survival in Human Serum." \textit{\textbf{Journal of Immunology}}, 199: ji1700877. https://doi.org/10.4049/jimmunol.1700877
    }% Ref
    {P6} % Number
  \cvpub
    {\textbf{MG Chevrette}, F Aicheler, O Kohlbacher, CR Currie, MH Medema. (2017). ``SANDPUMA: Ensemble Predictions of Nonribosomal Peptide Chemistry Reveals Biosynthetic Diversity across Actinobacteria." \textit{\textbf{Bioinformatics}}, 2017, 1–9. https://doi.org/10.1093/bioinformatics/btx400
    } % Ref
    {P5} % Number
  \cvpub
    {IJ Miller, \textbf{MG Chevrette}, JC Kwan. (2017). ``Interpreting Microbial Biosynthesis in the Genomic Age: Biological and Practical Considerations." \textit{\textbf{Marine Drugs}}, 15(6), 165. https://doi.org/10.3390/md15060165
    } % Ref
    {P4} % Number
  \cvpub
    {K Blin, T Wolf, \textbf{MG Chevrette}, X Lu, CJ Schwalen, SA Kautsar, HG Suarez Duran, ELC de los Santos, HUK Kim, M Nave, JS Dickschat, DA Mitchell, E Shelest, R Breitling, E Takano, SY Lee, T Weber, MH Medema. (2017). ``antiSMASH 4.0 - Improvements in Chemistry Prediction and Gene Cluster Boundary Identification." \textit{\textbf{Nucleic Acids Research}}, 1854(1), 1019–1037. https://doi.org/10.1093/nar/gkx319
    }  % Ref
    {P3} % Number
  \cvpub
    {GR Lewin, C Carlos, \textbf{MG Chevrette}, HA Horn, BR McDonald, RJ Stankey, BG Fox, CR Currie. (2016). ``Ecology and Evolution of Actinobacteria and their Bioenergy Applications." \textit{\textbf{Annual Review of Microbiology}}. 70: 235 -254. https://doi.org/10.1146/annurev-micro-102215-095748
    } % Ref
    {P2} % Number
  \cvpub
    {SS Johnson, \textbf{MG Chevrette}, BL Ehlmann, KC Benison. (2015). ``Insights from the Metagenome of an Acid Salt Lake: the Role of Biology in an Extreme Depositional Environment."  \textit{\textbf{PLOS ONE}}. 2015 Apr; 10(4):e0122869. https://doi.org/10.1371/journal.pone.0122869
    } % Ref
    {P1} % Number
\end{cvpubs}

\cvsection{Editorial Review Only}
\begin{cvpubs}
  \cvpub
    {\textbf{MG Chevrette}. (2018). ``Natuaral Products Reawakened: New Trends in Discovery and Development." \textit{\textbf{SIMB News Magazine}, Society for Industrial Microbiology and Biotechnology}, \textit{In press}. }  % Ref
    {E5} % Number
  \cvpub
    {DR Braun, \textbf{MG Chevrette}, D Acharya, CR Currie, SR Rajski, TS Bugni. (2018). ``Draft Genome of \textit{Micromonospora sp. WMMA1996}, a Marine Sponge-associated Bacterium." \textit{\textbf{Genome Announcements}}, 6(8), e00077-18.}  % Ref
    {E4} % Number
  \cvpub
    {DR Braun, \textbf{MG Chevrette}, D Acharya, CR Currie, SR Rajski, K Ritchie, TS Bugni. (2018). ``Complete Genome of \textit{Dietzia sp. WMMA184}, a Marine Coral-associated Bacterium." \textit{\textbf{Genome Announcements}}, 6(5), e01582-17.} % Ref
    {E3} % Number
  \cvpub
    {N Adnani, DR Braun, BR McDonald, \textbf{MG Chevrette}, CR Currie, TS Bugni. (2017). ``Draft Genome of \textit{Micromonospora sp. WMMB-235}, a Marine Ascidian-associated Bacterium." \textit{\textbf{Genome Announcements}}, 5(2), 1-2.} % Ref
    {E2} % Number
  \cvpub
  {N Adnani, DR Braun, BR McDonald, \textbf{MG Chevrette}, CR Currie, TS Bugni. (2016). ``Complete Genome Sequence of Rhodococcus sp. Strain WMMA185, a Marine Sponge-Associated Bacterium." \textit{\textbf{Genome Announcements}}, 4(6), 1–2.} % Ref
    {E1} % Number
\end{cvpubs}