%\newpage

\cvsection{\faBook\space Publications, Talks, \& Abstracts}

%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------

\cvsubsection{Peer-reviewed Publications}
\begin{cvpubs}

%\cvpub
%{\hspace{-1cm} Google scholar citations: 1065 \hspace{10mm} Google scholar h-index: 11} % Ref
%{}

\cvpub
{\hspace{-1cm} *\textit{Co-first author, contributed equally}} % Ref
{}

\cvpub
{EJN Helfrich*, R Ueoka*, \textbf{MG Chevrette*}, F Hemmerling, X Lu, S Leopold-Messner, AY Burch, SE Lindow, J Handelsman, J Piel, MH Medema. ``Evolution of combinatorial diversity in \textit{trans}-acyltransferase polyketide synthase assembly lines across bacteria." \textit{In press. \textbf{Nature Communications}.}}
{24}

\end{cvpubs} \begin{cvpubs}

\cvpub
{A Hurley, \textbf{MG Chevrette}, DD Acharya, GL Lozano, M Garavito, J Heinritz, L Balderrama, M Beebe, ML DenHartog, K Corinaldi, R Engels, A Gutierrez, O Jona, JHI Putnam, B Rhodes, T Tsang, S Hernandez, C Bascom-Slack, JE Blum, PA Price, D Davis, J Klein, J Pultorak, NL Sullivan, NJ Mouncey, PC Dorrestein, S Miller, NA Broderick, J Handelsman. ``Tiny Earth\: a big idea for STEM education and antibiotic discovery." \textit{In press. \textbf{mBio}.} \textbf{\colorhref{https://www.preprints.org/manuscript/202011.0250/v1}{Preprint available}}}
{23}

\cvpub
{MA Schorn*, S Verhoeven*, et al. [104 authors including \textbf{MG Chevrette}]. ``Standardized links between genomic and metabolomic data facilitate integrative mining." \textit{In press. \textbf{Nature Chemical Biology}.}}
{22}

\cvpub
{HE Ortega*, VB Lourenzon*, \textbf{MG Chevrette*}, LG Ferreira, M Zhao, RFR Alvarenga, WGP Melo, T Venâncio, DR Andes, CR Currie, AD Andricopulo, TS Bugni, MT Pupo. ``Antileishmanial macrolides from ant-associated \textit{Streptomyces} sp. ISID311." 2021. \textit{\textbf{Bioorganic \& Medicinal Chemistry}}. \textbf{\textit{\colorhref{https://doi.org/10.1016/j.bmc.2021.116016}{10.1016/j.bmc.2021.116016}}}}
{21}

\cvpub
{F Zhang, M Zhao, DR Braun, A Audhya, SS Ericksen, JS Piotrowski, J Nelson, J Peng, GE Ananiev, S Chanana, K Barns, J Fossen, \textbf{MG Chevrette}, IA Guzei, C Zhao, L Guo, W Tang, CR Currie, SR Rajski, DR Andes, TS Bugni. ``A marine microbiome antifungal targets urgent-threat drug-resistant fungi." 2020. \textit{\textbf{Science}}. \textbf{\textit{\colorhref{https://doi.org/10.1126/science.abd6919}{10.1126/science.abd6919}}} \linebreak
\textbf{[\textit{\colorhref{https://doi.org/10.1126/science.abf1675}{Highlighted by Science}}]}}
{20}

\cvpub
{Q Wu, K Throckmorton, M Maity, \textbf{MG Chevrette}, DR Braun, SR Rajski, CR Currie, MG Thomas, TS Bugni. ``Bacillibactins E and F from a marine sponge-associated \textit{Bacillus} sp." 2020. \textit{Journal of Natural Products}. \textbf{\textit{\colorhref{https://doi.org/10.1021/acs.jnatprod.0c01170}{10.1021/acs.jnatprod.0c01170}}}}
{19}

\cvpub
{F Zhang, TP Wyche, Y Zhu, DR Braun, J Yan, Y Ge, IA Guzei, \textbf{MG Chevrette}, CR Currie, MG Thomas, SR Rajski, TS Bugni. ``MS-derived isotopic fine structure reveals forazoline A as a thioketone-containing marine-derived natural product." 2020. \textit{\textbf{Organic Letters}}. \textbf{\textit{\colorhref{https://doi.org/10.1021/acs.orglett.9b04535}{10.1021/acs.orglett.9b04535}}}}
{18}

\cvpub
{\textbf{MG Chevrette}, K Guti\'{e}rrez-Garc\'{i}a, N Selem-Mojica, C Aguilar-Mart\'{i}nez, A Ya\~{n}ez-Olvera, HE Ramos-Aboites, PA Hoskisson, F Barona-G\'{o}mez. ``Evolutionary dynamics of natural product biosynthesis in bacteria." 2020. \textit{\textbf{Natural Product Reports}}. \textbf{\textit{\colorhref{https://doi.org/10.1039/c9np00048h}{10.1039/c9np00048h}}}}
{17}

\cvpub
{EJ Caldera*, \textbf{MG Chevrette*}, BR McDonald, CR Currie. ``Local adaptation of bacterial symbionts within a geographic mosaic of antibiotic coevolution." 2019. \textit{\textbf{Applied \& Environmental Microbiology}}. \textbf{\textit{\colorhref{https://doi.org/10.1128/AEM.01580-19}{10.1128/AEM.01580-19}}} \linebreak \textbf{[\textit{Cover Image for Issue}}]}
{16}

\cvpub
{\textbf{MG Chevrette}, C Carlos-Shanley, KB Louie, BP Bowen, TR Northen, CR Currie. ``Taxonomic and metabolic incongruence in the ancient genus \textit{Streptomyces}." 2019. \textit{\textbf{Frontiers in Microbiology}}. \textbf{\textit{\colorhref{https://doi.org/10.3389/fmicb.2019.02170}{10.3389/fmicb.2019.02170}}}}
{15}

\cvpub
{K Throckmorton*, V Vinnik*, R Chowdhury, TB Cook, \textbf{MG Chevrette}, CD Maranas, BF Pfleger, MG Thomas. ``Directed evolution of an adenylation domain specificity code." 2019. \textit{\textbf{ACS Chemical Biology}}. \textbf{\textit{\colorhref{https://doi.org/10.1021/acschembio.9b00532}{10.1021/acschembio.9b00532}}}}
{14}

\cvpub
{J Yan, \textbf{MG Chevrette}, D Braun, MK Harper, CR Currie, TS Bugni. ``Madurastatin D1 and D2, oxazoline containing siderophores isolated from an \textit{Actinomadura} sp." 2019. \textit{\textbf{Organic Letters}}. \textbf{\textit{\colorhref{https://doi.org/10.1021/acs.orglett.9b02159}{10.1021/acs.orglett.9b02159}}}}
{13}

\cvpub
{\textbf{MG Chevrette*}, JR Bratburd*, CR Currie, RM Stubbendieck. ``Experimental microbiomes: models not to scale." 2019. \textit{\textbf{mSystems}}. \textbf{\textit{\colorhref{https://doi.org/10.1128/mSystems.00175-19}{10.1128/mSystems.00175-19}}}}
{12}

\cvpub
{\textbf{MG Chevrette}, CM Carlson, HE Ortega, C Thomas, GE Ananiev, KJ Barns, AJ Book, J Cagnazzo, C Carlos, W Flanigan, KJ Grubbs, HA Horn, FM Hoffmann, JL Klassen, JJ Knack, GR Lewin, BR McDonald, L Muller, WGP Melo, AA Pinto-Tom\'{a}s, A Schmitz, E Wendt-Pienkowski, S Wildman, M Zhao, F Zhang, TS Bugni, DR Andes, MT Pupo, CR Currie. ``The antimicrobial potential of \textit{Streptomyces} from insect microbiomes." 2019. \textit{\textbf{Nature Communications}}. \textbf{\textit{\colorhref{https://doi.org/10.1038/s41467-019-08438-0}{10.1038/s41467-019-08438-0}}} \linebreak \textbf{[\textit{\colorhref{https://www.npr.org/sections/health-shots/2019/02/13/694118623/bugs-vs-superbugs-insects-offer-promise-in-fight-against-antibiotic-resistance}{Highlighted by NPR}}]}}
{11}

\cvpub
{RM Stubbendieck, DS May, \textbf{MG Chevrette}, MI Temkin, E Wendt-Pienkowski, J Cagnazzo, CM Carlson, JE Gern, CR Currie. ``Competition among nasal bacteria suggests a role for siderophore-mediated interactions in shaping the human nasal microbiota." 2019. \textit{\textbf{Applied \& Environmental Microbiology}}. \textbf{\textit{\colorhref{https://doi.org/10.1128/AEM.02406-18}{10.1128/AEM.02406-18}}}}
{10}

\cvpub
{N Liu,* H Li,* \textbf{MG Chevrette}, L Zhang, L Cao, H Zhou, X Zhou, Z Zhou, PB Pope, CR Currie, Y Huang, Q Wang. 2019. ``Functional metagenomics reveals polysaccharide-degrading gene clusters and cellobiose utilization pathways in gut microbiota of a wood-feeding termite." \textit{\textbf{ISME Journal}}. \textbf{\textit{\colorhref{https://doi.org/10.1038/s41396-018-0255-1}{10.1038/s41396-018-0255-1}}}}
{9}

\cvpub
{\textbf{MG Chevrette}, CR Currie. ``Emerging evolutionary paradigms in antibiotic discovery." 2019. \textit{\textbf{Journal of Industrial Microbiology \& Biotechnology}}. \textbf{\textit{\colorhref{https://doi.org/10.1007/s10295-018-2085-6}{10.1007/s10295-018-2085-6}}}}
{8}

\cvpub
{N Adnani, \textbf{MG Chevrette}, SN Adibhatla, F Zhang, Q Yu, D Braun, J Nelson, SW Simpkins, BR McDonald, CL Myers, J Piotrowski, C Thompson, CR Currie, L Li, SR Rajski, TS Bugni. ``Co-culture of marine invertebrate-associated bacteria and interdisciplinary technologies enable biosynthesis and discovery of a new antibiotic, keyicin." 2017. \textit{\textbf{ACS Chemical Biology}}.  \textbf{\textit{\colorhref{https://doi.org/10.1021/acschembio.7b00688}{10.1021/acschembio.7b00688}}} \linebreak \textbf{[\textit{\colorhref{https://www.nature.com/articles/d41586-017-07231-7}{Highlighted by Nature}}]}}
{7}

\cvpub
{AF Sanchez-Larrayoz, NM Elshamy, \textbf{MG Chevrette}, Y Fu, P Giunta, RG Spallanzani, K Ravi, GB Pier, S Lory, T Maira-Litr\'{a}n. ``Complexity of complement-resistance factors expressed by \textit{Acinetobacter baumannii} needed for survival in human serum." 2017. \textit{\textbf{Journal of Immunology}}. \textbf{\textit{\colorhref{https://doi.org/10.4049/jimmunol.1700877}{10.4049/jimmunol.1700877}}}}
{6}

\cvpub
{\textbf{MG Chevrette}, F Aicheler, O Kohlbacher, CR Currie, MH Medema. ``SANDPUMA: Ensemble predictions of nonribosomal peptide chemistry reveals biosynthetic diversity across Actinobacteria." 2017. \textit{\textbf{Bioinformatics}}. \textbf{\textit{\colorhref{https://doi.org/10.1093/bioinformatics/btx400}{10.1093/bioinformatics/btx400}}}}
{5}

\end{cvpubs} \begin{cvpubs}

\cvpub
{IJ Miller, \textbf{MG Chevrette}, JC Kwan. (2017). ``Interpreting microbial biosynthesis in the genomic age: Biological and practical considerations." 2017. \textit{\textbf{Marine Drugs}}. \textbf{\textit{\colorhref{https://doi.org/10.3390/md15060165}{10.3390/md15060165}}} \linebreak \textbf{[\textit{Cover Image for Issue}]}}
{4}

\cvpub
{K Blin, T Wolf, \textbf{MG Chevrette}, X Lu, CJ Schwalen, SA Kautsar, HG Suarez Duran, ELC de los Santos, HUK Kim, M Nave, JS Dickschat, DA Mitchell, E Shelest, R Breitling, E Takano, SY Lee, T Weber, MH Medema. ``antiSMASH 4.0 - Improvements in chemistry prediction and gene cluster boundary identification." 2017. \textit{\textbf{Nucleic Acids Research}}. \textbf{\textit{\colorhref{https://doi.org/10.1093/nar/gkx319}{10.1093/nar/gkx319}}}}
{3}

\cvpub
{GR Lewin, C Carlos, \textbf{MG Chevrette}, HA Horn, BR McDonald, RJ Stankey, BG Fox, CR Currie. ``Ecology and evolution of Actinobacteria and their bioenergy applications." 2016. \textit{\textbf{Annual Review of Microbiology}}. \textbf{\textit{\colorhref{https://doi.org/10.1146/annurev-micro-102215-095748}{10.1146/annurev-micro-102215-095748}}}}
{2}

\cvpub
{SS Johnson, \textbf{MG Chevrette}, BL Ehlmann, KC Benison. ``Insights from the metagenome of an acid salt lake: The role of biology in an extreme depositional environment."  2015. \textit{\textbf{PLOS ONE}}. \textbf{\textit{\colorhref{https://doi.org/10.1371/journal.pone.0122869}{10.1371/journal.pone.0122869}}}}
{1}

\end{cvpubs}

%--------------------------------

\cvsubsection{Book Chapters}
\begin{cvpubs}

\cvpub
{\textbf{MG Chevrette}, PA Hoskisson, F Barona-G\'{o}mez. ``Enzyme evolution in secondary metabolism." 2019. \textit{\textbf{Comprehensive Natural Products III: Chemistry and Biology}}. \textbf{\textit{\colorhref{https://doi.org/10.1016/B978-0-12-409547-2.14712-2}{10.1016/B978-0-12-409547-2.14712-2}}}}
{1}

\end{cvpubs}

%--------------------------------

\cvsubsection{Publications, Editorial Review Only}
\begin{cvpubs}

\cvpub
{\textbf{MG Chevrette}, J Handelsman. ``From metagenomes to molecules: Innovations in functional metagenomics unlock hidden chemistry in the human microbiome." 2020. \textit{\textbf{Biochemistry}}. \textbf{\textit{\colorhref{https://doi.org/10.1021/acs.biochem.0c00033}{10.1021/acs.biochem.0c00033}}}}
{6}

\cvpub
{\textbf{MG Chevrette}. ``Natural products reawakened: New trends in discovery and development." 2018. \textit{\textbf{SIMB News Magazine}, Society for Industrial Microbiology and Biotechnology}. }
{5}

\cvpub
{DR Braun, \textbf{MG Chevrette}, D Acharya, CR Currie, SR Rajski, TS Bugni. ``Draft genome of \textit{Micromonospora sp. WMMA1996}, a marine sponge-associated bacterium." 2018. \textit{\textbf{Genome Announcements}}. \textbf{\textit{\colorhref{https://doi.org/10.1128/genomeA.00077-18}{10.1128/genomeA.00077-18}}}}
{4}

\cvpub
{DR Braun, \textbf{MG Chevrette}, D Acharya, CR Currie, SR Rajski, K Ritchie, TS Bugni. ``Complete genome of \textit{Dietzia sp. WMMA184}, a marine coral-associated bacterium." 2018. \textit{\textbf{Genome Announcements}}. \textbf{\textit{\colorhref{https://doi.org/10.1128/genomeA.01582-17}{10.1128/genomeA.01582-17}}}}
{3}

\cvpub
{N Adnani, DR Braun, BR McDonald, \textbf{MG Chevrette}, CR Currie, TS Bugni. ``Draft genome of \textit{Micromonospora sp. WMMB-235}, a marine ascidian-associated bacterium." 2017. \textit{\textbf{Genome Announcements}}. \textbf{\textit{\colorhref{https://doi.org/10.1128/genomeA.01369-16}{10.1128/genomeA.01369-16}}}}
{2}

\cvpub
{N Adnani, DR Braun, BR McDonald, \textbf{MG Chevrette}, CR Currie, TS Bugni. ``Complete genome sequence of \textit{Rhodococcus sp. strain WMMA185}, a marine sponge-associated bacterium." 2016. \textit{\textbf{Genome Announcements}}. \textbf{\textit{\colorhref{https://doi.org/10.1128/genomeA.01406-16}{10.1128/genomeA.01406-16}}}}
{1}

\end{cvpubs}

%--------------------------------

\cvsubsection{Patents}
\begin{cvpubs}

\cvpub
{DC Gray, E Li, BR Bowman, GL Verdine, K Robison, \textbf{MG Chevrette}, D Udwary, PS Wang, A Li, JP Morgenstern. Compositions and methods for the production of compounds. Priority 2016-10-28, filed 2017-10-27, published 2019-08-29. \textbf{\textit{\colorhref{https://patents.google.com/patent/US20190264184A1/en}{US20190264184A1}}}}
{1}

\end{cvpubs}

%--------------------------------

\cvsubsection{Preprints, Submitted, and Under Review}
\begin{cvpubs}

\cvpub
{GR Lewin, NM Davis, BR McDonald, AJ Book, \textbf{MG Chevrette}, S Suh, A Boll, CR Currie. ``Long-term cellulose enrichment selects for highly cellulolytic consortia and competition for public goods." \textit{Submitted. \textbf{\colorhref{https://doi.org/10.1101/2020.09.18.304485}{Preprint available}}}}
{3}

\cvpub
{J Yan, Q Wu, EJN Helfrich, \textbf{MG Chevrette}, DR Braun, H Heyman,  GE Ananiev, SR Rajski, CR Currie, J Clardy, TS Bugni. ``Bacillimidazoles A−F, imidazolium-containing antibacterial compounds isolated from a marine \textit{Bacillus}." \textit{Submitted.}}
{2}

\cvpub
{BR McDonald, \textbf{MG Chevrette}, JL Klassen, HA Horn, EJ Caldera, E Wendt-Pienkowski, MJ Cafaro, AC Ruzzini, EB Van Arnam, GM Weinstock, NM Gerardo, M Poulsen, G Suen, J Clardy, CR Currie. ``Biogeography and microscale diversity shape the biosynthetic potential of fungus-growing ant-associated \textit{Pseudonocardia}." \textit{In revision. \textbf{\colorhref{https://doi.org/10.1101/545640}{Preprint available}}}}
{1}

\end{cvpubs}

%--------------------------------
%\newpage

\cvsubsection{Invited Talks}
\begin{cvpubs}

\cvpub
{TBD. International Symposium on the Biology of Actinomycetes. Toronto, ON. Originally scheduled for Jun 23, 2020. Postponed due to COVID-19.}
{12}

\cvpub
{``Evolution of antibiotic biosynthesis as a framework for drug discovery." Biotechnology Institute Seminar Series. University of Minnesota. St. Paul, MN (remote). Dec 17, 2020.}
{11}

\cvpub
{``Evolution of antibiotic biosynthesis as a framework for drug discovery." Whitney Laboratory for Marine Bioscience Seminar Series. University of Florida. Gainesville, FL (remote). Sep 25, 2020.}
{10}

\cvpub
{``The Earth’s bounty: antibiotic discovery from soil." Gairdner Symposium, McMaster University. Hamilton, ON. Nov 15, 2019.}
{9}

\cvpub
{``Drugs from bugs of bugs: a novel source for antimicrobials." American Society for Microbiology Microbe. San Francisco, CA. Jun 21, 2019.}
{8}

\cvpub
{``Mining microbiomes for antimicrobials." Synthetic Biology for Natural Products Conference. Puerto Vallarta, Mexico. Jun 02, 2019.}
{7}

\end{cvpubs} \begin{cvpubs}

\cvpub
{``Drugs from bugs of bugs: microbiomes as a source of new antibiotics." Wisconsin Institute for Discovery. Madison, WI. Jan 24, 2019.}
{6}

\cvpub
{``Drugs \& bugs of bugs: insect microbiomes as a source of new antibiotics."  McMaster University. Hamilton, ON. Jun 21, 2018.}
{5}

\cvpub
{``Host-associated microbes as a source of new antimicrobials." Natural Product Discovery \& Development in the Genomic Era, Society for Industrial Microbiology \& Biotechnology. Clearwater Beach, FL. Jan 22, 2018.}
{4}

\cvpub
{``Natural natural products: Leveraging chemical ecology in the search for new drugs." Evolution Seminar Series, JF Crow Institute for the Study of Evolution. Madison, WI. Oct 26, 2017.}
{3}

\cvpub
{``Computational insights into the diverse nonribosomal peptide chemistry of Actinobacteria." Synthetic Biology for Natural Products Conference. Cancun, Mexico. Mar 6, 2017. \linebreak \textbf{[\textit{\colorhref{https://doi.org/10.1021/acssynbio.7b00132}{Highlighted in ACS Synthetic Biology}}]}}
{2}

\cvpub
{``Darwinian drug discovery: Chemical ecology at fine and coarse evolutionary scales." International Chemical Biology Society Annual Conference. Madison, WI. Oct 24, 2016. \linebreak \textbf{[\textit{\colorhref{https://doi.org/10.1021/acschembio.7b00205}{Highlighted in ACS Chemical Biology}}]}}
{1}

\end{cvpubs}

%--------------------------------

\cvsubsection{Internal Seminars}
\begin{cvpubs} 

\cvpub
{``Using antiSMASH as both an antibiotic discovery \& teaching tool." Tiny Earth Symposium 2020, UW-Madison. Jun 12, 2020.}
{6}

\cvpub
{``Tiny Earth Chemistry Hub: the next stop for your samples." Tiny Earth Symposium 2019, UW-Madison. Jul 10, 2019.}
{5}

\cvpub
{``Drugs \& bugs of bugs: Insect microbiomes as a source of new antibiotics." Genetics Colloquium, UW-Madison. Aug 8, 2018.}
{4}

\cvpub
{``Host-microbe interactions as as a source of new antimicrobials
." Highlights at the Chemistry-Biology Interface Colloquium, UW-Madison. Dec 12, 2017.}
{3}

\cvpub
{``Genome-based natural product discovery, modular biosynthesis, \& applications." Highlights at the Chemistry-Biology Interface Colloquium, UW-Madison. Feb 2, 2017.}
{2}

\cvpub
{``Genome assembly: Tools \& analysis." Computational Biology, Ecology, \& Evolution (ComBEE), UW-Madison. Apr 27, 2016.}
{1}

\end{cvpubs}

%--------------------------------

\cvsubsection{Abstracts}
\begin{cvpubs}

\cvpub
{\underline{\textbf{MG Chevrette}}, A Hurley, J Handelsman. ``Tiny Earth Genomics: Mining bacterial genomes for antibiotic chemistry." Presented at: Wisconsin Institute for Discovery Illuminating Connections; Madison, WI; Feb 12, 2020.}
{31}

\cvpub
{A Hurley, DD Acharya, \underline{\textbf{MG Chevrette}}, W Chezem, G Lozano, M Garavito, J Heinritz, L Balderrama, M Beebe, M DenHartog, K Corinaldi, R Engels, A Gutierrez, O Jona, J Putnam, B Rhodes, T Tsang, S Hernandez, C Bascom-Slack, D Davis, S Miller, N Broderick, J Handelsman. ``Tiny Earth Chemistry Hub: Command center for studentsourcing antibiotic discovery." Presented at: Wisconsin Institute for Discovery Illuminating Connections; Madison, WI; Feb 12, 2020.}
{30}

\cvpub
{\underline{\textbf{MG Chevrette}}, D Acharya, A Hurley, M Beebe, M Garavito, S Miller, J Handelsman. ``Tiny Earth Chemistry Hub: From soil to antibiotics." Presented at: Tiny Earth Symposium; Madison, WI; Jul 10, 2019.}
{29}

\cvpub
{\underline{K Throckmorton}, V Vinnik, TB Cook, R Chowdhury, \textbf{MG Chevrette}, CD Maranas, BF Pfleger, MG Thomas. ``Directed evolution of an adenylation domain specificity code." Presented at: Synthetic Biology for Natural Products Conference; Puerto Vallarta, Mexico; Jun 2, 2019.}
{28}

\cvpub
{\underline{CL Hansen}, \textbf{MG Chevrette}, M Selvaraj, A Vasquez Echeverri, D Maldonado Perez, C Eno, J Hernandez-Ortiz, F Pelegri. ``Helical supramolecular assembly of a germline specific membraneless organelle." Presented at: Phase Separation in Biology \& Disease; New York, NY; Feb 20, 2019.}
{27}

\cvpub
{\underline{\textbf{MG Chevrette}}, CM Carlson, H Ortega, F Zhang, KJ Grubbs, MT Pupo, TS Bugni, DR Andes, CR Currie. ``Insect-associated \textit{Streptomyces} are a rich source of new antimicrobials." Presented at: Beneficial Microbes; Madison, WI; Jul 9, 2018.}
{26}

\cvpub
{\underline{HA Horn}, E Gemperline, K Delaney, \textbf{MG Chevrette}, L Li, CR Currie. ``Host specificity influences chemical resopnse in \textit{in vivo} symbiotic interactions." Presented at: Beneficial Microbes; Madison, WI; Jul 9, 2018.}
{25}

\cvpub
{\underline{BR McDonald}, \textbf{MG Chevrette}, J Klassen, HA Horn, EJ Caldera, E Wendt-Pienkowski, MJ Cafaro, AC Ruzzini, EB Van Arnam, GM Weinstock, NM Gerardo, MG Poulsen, G Suen, J Clardy, CR Currie. ``Biogeography and microscale diversity shapes the biosynthetic potential of fungus-growing ant associated \textit{Pseudonocardia}." Presented at: Beneficial Microbes; Madison, WI; Jul 9, 2018.}
{24}

\cvpub
{\underline{\textbf{MG Chevrette}}, CM Carlson, H Ortega, F Zhang, KJ Grubbs, MT Pupo, TS Bugni, DR Andes, CR Currie. ``Insect-associated \textit{Streptomyces} are a rich source of new antimicrobials with activity against resistant human pathogens." Presented at: Perlman Antibiotic Discovery and Development Symposium; Madison, WI; Apr 27, 2018.}
{23}

\cvpub
{\underline{DD Acharya}, IJ Miller, Y Cui, DR Braun, \textbf{MG Chevrette}, M Berres, L Li, J Kwan, CR Currie, TS Bugni. ``Chemical cross-talk in bacterial co-cultures affects differential gene expression and antibiotic production." Presented at: Perlman Antibiotic Discovery and Development Symposium; Madison, WI; Apr 27, 2018.}
{22}

\cvpub
{\underline{R Zarnowski}, \textbf{MG Chevrette}, E Dominguez, DR Andes. ``Modeling high-throughput proteomics into predictive metabolomics - A novel tool for studies of medical device-associated \textit{Candida spp.} biofilm infections." Presented at: Metabolomics Circle 2017 - Bioanylytical \& Omics Science, Wrocław, Poland; Nov 18, 2017.}
{21}

\end{cvpubs} \begin{cvpubs}

\cvpub
{\underline{D Acharya}, N Adnani, D Braun, IJ Miller, Q Yu, \textbf{MG Chevrette}, M Berres, CR Currie, L Li, JC Kwan, TS Bugni. ``Chemical cross-talk in bacterial co-cultures affects differential gene expression and antibiotic production." Presented at: American Society for Pharmacognosy Annual Meeting, Portland, OR; Jul 30, 2017.}
{20}

\cvpub
{AF Sanchez-Larrayoz, NM Elhosseiny, \textbf{MG Chevrette}, Y Fu, P Giunta, G Spallanzani, GB Pier, S Lory, \underline{T Maira-Litr\'{a}n}. ``The membrane lipid asymmetry transport system plays a key role in protecting \textit{Acinetobacter baumannii} against killing by human complement via the alternative pathway." Presented at: American Society for Microbiology Microbe, New Orleans, LA; Jun 2, 2017.}
{19}

\cvpub
{\underline{\textbf{MG Chevrette}}, CM Carlson, C Thomas, TS Bugni, DR Andes, CR Currie. ``Evolutionary trends in secondary metabolism reveal insect-associated \textit{Streptomyces} as an underexploited antibiotic resource." Presented at: Perlman Antibiotic Discovery and Development Symposium; Madison, WI; Mar 31, 2017.}
{18}

\cvpub
{\underline{EJ Caldera}, \textbf{MG Chevrette}, CR Currie. ``The geographic mosaic of antibiotic coevolution in a bacterial symbiont of the fungus-farming ant \textit{Apterostigma dentigerum}." Presented at: Perlman Antibiotic Discovery and Development Symposium; Madison, WI; Mar 31, 2017.}
{17}

\cvpub
{\underline{J Bratburd}, C Keller, E Vivas, \textbf{MG Chevrette}, F Rey, L Li, CR Currie. ``The human gut microbiota metabolomic response to infection." Presented at: Perlman Antibiotic Discovery and Development Symposium; Madison, WI; Mar 31, 2017.}
{16}

\cvpub
{\textbf{\underline{MG Chevrette}}, CR Currie, MH Medema.  ``prediCAT: An accurate predictive method for substrate specificity of nonribosomal peptide synthetase adenylation domains." Presented at: Kenneth B. Raper Symposium on Microbial Research; Madison, WI; Sep 2, 2016.}
{15}

\cvpub
{\underline{J Bratburd}, BR McDonald, \textbf{MG Chevrette}, JL Klassen, HA Horn, CR Currie. ``Comparative genomics of fungus-growing ant-associated \textit{Pseudonocardia}." Presented at: Kenneth B. Raper Symposium on Microbial Research; Madison, WI; Sep 2, 2016.}
{14}

\cvpub
{\underline{HA Horn}, E Gemperline, \textbf{MG Chevrette}, BR Mcdonald, J Bratburd, E Mevers, J Clardy, L Li, CR Currie. ``Mass spectrometry imaging reveals differential chemical response to pathogens in an ancient ant-microbe symbiosis." Presented at: ISME International Symposium on Microbial Ecology; Montreal, QC, Canada; Aug 21-26, 2016.}
{13}

\cvpub
{\textbf{\underline{MG Chevrette}}, CR Currie, MH Medema.  ``Computational predictions of substrate specificity in nonribosomal peptide synthetases through comparative adenylation domain trees." Presented at: American Society for Microbiology Microbe; Boston, MA; Jun 16-20, 2016.}
{12}

\cvpub
{\underline{SS Johnson}, ML Soni, DJ Collins, KC Benison, MR Mormile, \textbf{MG Chevrette}, BL Ehlmann. ``Biosignatures in mars analog acid salt lakes." Presented at: USRA Biosignature, Preservation and Detection in Mars Analog Environments; Lake Tahoe, Nevada; May 16-19, 2016.}
{11}

\cvpub
{\textbf{\underline{MG Chevrette}}, C Carlson, C Thomas, TS Bugni, CR Currie. ``Multifaceted antibiotic profiling across Actinomycete chemical ecology." Presented at: Perlman Antibiotic Discovery and Development Symposium; Madison, WI; Apr 29, 2016.}
{10}

\cvpub
{\underline{N Adnani}, S Adibhatla, E Vazquez-Rivera, GA Ellis, D Braun, \textbf{MG Chevrette}, BR McDonald, C Thompson, JS Piotrowski, Q Yu, L Li, CR Currie, TS Bugni. ``Driving production of novel natural products through marine microbial interspecies interactions." Presented at: Gordon Marine Natural Products; Ventura, CA; Mar 6-11, 2016.}
{9}

\cvpub
{\textbf{\underline{MG Chevrette}}, DW Udwary, CR Currie, SS Johnson. ``Functional classification and secondary metabolism of an extreme metagenome." Presented at: Kenneth B. Raper Symposium on Microbial Research; Madison, WI; Sep 1, 2015.}
{8}

\cvpub
{\textbf{\underline{MG Chevrette}}, BL Ehlmann, KC Benison, SS Johnson. ``Microbial diversity and biosynthetic potential of an extreme sediment metagenome." Presented at: Gordon Applied and Environmental Microbiology; South Hadley, MA; Jul 12-17, 2015.}
{7}

\cvpub
{\textbf{\underline{MG Chevrette}}, M Vinacur, T Maira-Litr\'{a}n. ``Transposon-directed insertion site sequencing reveals \textit{in vivo} fitness factors in \textit{Acinetobacter baumannii} lung infections." Presented at: Boston Bacterial Meeting; Cambridge, MA; Jun 18-19, 2015.}
{6}

\cvpub
{\underline{DW Udwary}, K Robison, \textbf{MG Chevrette}, GL Verdine. ``Lessons from long read assembly of 100+ Actinomycete genomes." Presented at: Gordon Marine Natural Products; Ventura, CA; Mar 2-7, 2014.}
{5}

\cvpub
{\underline{K Robison}, DW Udwary, \textbf{MG Chevrette}, GL Verdine. ``Long read assembly of >100 Actinomycete genomes." Presented at: Advances in Genome Biology \& Technology; Marco Island, FL; Feb 12-15, 2014.}
{4}

\cvpub
{\underline{S Young}, S Steelman, R Daza, \textbf{MG Chevrette}, R Lintner, S Gnerre, A Berlin, B Walker, C Nusbaum, R Nicol. ``Generation of high-quality draft assemblies with a single sequencing library." Presented at: Sequencing, Finishing, Analysis in the Future; Santa Fe, NM; May 29-31, 2013.}
{3}

\cvpub
{\underline{S Steelman}, R Daza, \textbf{MG Chevrette}, P Kompella, P Trang, T Surabian, R Lintner, CZ Zhang, J Jung, M Meyerson, C Nusbaum, R Nicol. ``Automated low input mate-pair library construction for Illumina sequencing." Presented at: Advances in Genome Biology \& Technology; Marco Island, FL; Feb 15-18, 2012.}
{2}

\cvpub
{S Steelman, R Daza, \underline{\textbf{MG Chevrette}}, P Kompella, P Trang, T Surabian, R Lintner, R Nicol. ``Microbial mate-pair library construction for de novo detection of structural rearrangements." Presented at: Broad Institute Symposium; Boston, MA; Nov 7-8, 2011.}
{1}

\end{cvpubs}