%\newpage

\cvsection {\faMicrophone\space Talks \& Abstracts}

\cvsubsection{Invited Talks} \vspace{-2mm}

\begin{cvpubs}

\cvpub
{\hspace{-1cm} \textit{Total: 14}}
{}

\cvpub
{Dynamic secondary metabolism in a model rhizosphere community. International Symposium on the Biology of Actinomycetes. Toronto, ON. Jun 20, 2022.}
{1}

\cvpub
{Microbial secondary metabolism: from evolutionary genomics to
community ecology. Latin American Workshop on Genome Mining of Natural Products. Guanajuato, Mexico. Jun 15, 2022.}
{2}

\cvpub
{Dynamic secondary metabolism in a model rhizosphere community. Synthetic Biology for Natural Products Conference. Cancun, Mexico. May 18, 2022.}
{3}

\cvpub
{``Evolution of antibiotic biosynthesis as a framework for drug discovery." Biotechnology Institute Seminar Series. University of Minnesota. St. Paul, MN (remote). Dec 17, 2020.}
{4}

\cvpub
{``Evolution of antibiotic biosynthesis as a framework for drug discovery." Whitney Laboratory for Marine Bioscience Seminar Series. University of Florida. Gainesville, FL (remote). Sep 25, 2020.}
{5}

\cvpub
{``The Earth’s bounty: antibiotic discovery from soil." Gairdner Symposium, McMaster University. Hamilton, ON. Nov 15, 2019.}
{6}

\cvpub
{``Drugs from bugs of bugs: a novel source for antimicrobials." American Society for Microbiology Microbe. San Francisco, CA. Jun 21, 2019.}
{7}

\cvpub
{``Mining microbiomes for antimicrobials." Synthetic Biology for Natural Products Conference. Puerto Vallarta, Mexico. Jun 02, 2019.}
{8}

\cvpub
{``Drugs from bugs of bugs: microbiomes as a source of new antibiotics." Wisconsin Institute for Discovery. Madison, WI. Jan 24, 2019.}
{9}

\cvpub
{``Drugs \& bugs of bugs: insect microbiomes as a source of new antibiotics."  McMaster University. Hamilton, ON. Jun 21, 2018.}
{10}

\cvpub
{``Host-associated microbes as a source of new antimicrobials." Natural Product Discovery \& Development in the Genomic Era, Society for Industrial Microbiology \& Biotechnology. Clearwater Beach, FL. Jan 22, 2018.}
{11}

\cvpub
{``Natural natural products: Leveraging chemical ecology in the search for new drugs." Evolution Seminar Series, JF Crow Institute for the Study of Evolution. Madison, WI. Oct 26, 2017.}
{12}

\cvpub
{``Computational insights into the diverse nonribosomal peptide chemistry of Actinobacteria." Synthetic Biology for Natural Products Conference. Cancun, Mexico. Mar 6, 2017. \linebreak \textbf{[\textit{\colorhref{https://doi.org/10.1021/acssynbio.7b00132}{Highlighted in ACS Synthetic Biology}}]}}
{13}

\cvpub
{``Darwinian drug discovery: Chemical ecology at fine and coarse evolutionary scales." International Chemical Biology Society Annual Conference. Madison, WI. Oct 24, 2016. \linebreak \textbf{[\textit{\colorhref{https://doi.org/10.1021/acschembio.7b00205}{Highlighted in ACS Chemical Biology}}]}}
{14}

\end{cvpubs}

%--------------------------------

\cvsubsection{Internal Seminars} \vspace{-2mm}

\begin{cvpubs} 

\cvpub
{\hspace{-1cm} \textit{Total: 6}}
{}

\cvpub
{``Using antiSMASH as both an antibiotic discovery \& teaching tool." Tiny Earth Symposium 2020, UW-Madison. Jun 12, 2020.}
{1}

\cvpub
{``Tiny Earth Chemistry Hub: the next stop for your samples." Tiny Earth Symposium 2019, UW-Madison. Jul 10, 2019.}
{2}

\cvpub
{``Drugs \& bugs of bugs: Insect microbiomes as a source of new antibiotics." Genetics Colloquium, UW-Madison. Aug 8, 2018.}
{3}

\cvpub
{``Host-microbe interactions as as a source of new antimicrobials
." Highlights at the Chemistry-Biology Interface Colloquium, UW-Madison. Dec 12, 2017.}
{4}

\cvpub
{``Genome-based natural product discovery, modular biosynthesis, \& applications." Highlights at the Chemistry-Biology Interface Colloquium, UW-Madison. Feb 2, 2017.}
{5}

\cvpub
{``Genome assembly: Tools \& analysis." Computational Biology, Ecology, \& Evolution (ComBEE), UW-Madison. Apr 27, 2016.}
{6}

\end{cvpubs}

%--------------------------------

\cvsubsection{Abstracts} \vspace{-2mm}

\begin{cvpubs}

\cvpub
{\hspace{-1cm} \textit{Total: 32; Listed below: 2017--present}}
{}

\cvpub
{\underline{S Magesh}, A Hurley, JF Nepper, \textbf{MG Chevrette}, J Handelsman. ``Genetic determinants of surface colonization by the rhizosphere bacterium \textit{Flavobacterium johnsoniae}." Presented at: World Microbe Forum; Online; Jun 20, 2021.}
{1}

\cvpub
{\underline{\textbf{MG Chevrette}}, A Hurley, J Handelsman. ``Tiny Earth Genomics: Mining bacterial genomes for antibiotic chemistry." Presented at: Wisconsin Institute for Discovery Illuminating Connections; Madison, WI; Feb 12, 2020.}
{2}

\end{cvpubs} \begin{cvpubs}

\cvpub
{A Hurley, DD Acharya, \underline{\textbf{MG Chevrette}}, W Chezem, G Lozano, M Garavito, J Heinritz, L Balderrama, M Beebe, M DenHartog, K Corinaldi, R Engels, A Gutierrez, O Jona, J Putnam, B Rhodes, T Tsang, S Hernandez, C Bascom-Slack, D Davis, S Miller, N Broderick, J Handelsman. ``Tiny Earth Chemistry Hub: Command center for studentsourcing antibiotic discovery." Presented at: Wisconsin Institute for Discovery Illuminating Connections; Madison, WI; Feb 12, 2020.}
{3}

\cvpub
{\underline{\textbf{MG Chevrette}}, D Acharya, A Hurley, M Beebe, M Garavito, S Miller, J Handelsman. ``Tiny Earth Chemistry Hub: From soil to antibiotics." Presented at: Tiny Earth Symposium; Madison, WI; Jul 10, 2019.}
{4}

\cvpub
{\underline{K Throckmorton}, V Vinnik, TB Cook, R Chowdhury, \textbf{MG Chevrette}, CD Maranas, BF Pfleger, MG Thomas. ``Directed evolution of an adenylation domain specificity code." Presented at: Synthetic Biology for Natural Products Conference; Puerto Vallarta, Mexico; Jun 2, 2019.}
{5}

\cvpub
{\underline{CL Hansen}, \textbf{MG Chevrette}, M Selvaraj, A Vasquez Echeverri, D Maldonado Perez, C Eno, J Hernandez-Ortiz, F Pelegri. ``Helical supramolecular assembly of a germline specific membraneless organelle." Presented at: Phase Separation in Biology \& Disease; New York, NY; Feb 20, 2019.}
{6}

\cvpub
{\underline{\textbf{MG Chevrette}}, CM Carlson, H Ortega, F Zhang, KJ Grubbs, MT Pupo, TS Bugni, DR Andes, CR Currie. ``Insect-associated \textit{Streptomyces} are a rich source of new antimicrobials." Presented at: Beneficial Microbes; Madison, WI; Jul 9, 2018.}
{7}

\cvpub
{\underline{HA Horn}, E Gemperline, K Delaney, \textbf{MG Chevrette}, L Li, CR Currie. ``Host specificity influences chemical resopnse in \textit{in vivo} symbiotic interactions." Presented at: Beneficial Microbes; Madison, WI; Jul 9, 2018.}
{8}

\cvpub
{\underline{BR McDonald}, \textbf{MG Chevrette}, J Klassen, HA Horn, EJ Caldera, E Wendt-Pienkowski, MJ Cafaro, AC Ruzzini, EB Van Arnam, GM Weinstock, NM Gerardo, MG Poulsen, G Suen, J Clardy, CR Currie. ``Biogeography and microscale diversity shapes the biosynthetic potential of fungus-growing ant associated \textit{Pseudonocardia}." Presented at: Beneficial Microbes; Madison, WI; Jul 9, 2018.}
{9}

\cvpub
{\underline{\textbf{MG Chevrette}}, CM Carlson, H Ortega, F Zhang, KJ Grubbs, MT Pupo, TS Bugni, DR Andes, CR Currie. ``Insect-associated \textit{Streptomyces} are a rich source of new antimicrobials with activity against resistant human pathogens." Presented at: Perlman Antibiotic Discovery and Development Symposium; Madison, WI; Apr 27, 2018.}
{10}

\cvpub
{\underline{DD Acharya}, IJ Miller, Y Cui, DR Braun, \textbf{MG Chevrette}, M Berres, L Li, J Kwan, CR Currie, TS Bugni. ``Chemical cross-talk in bacterial co-cultures affects differential gene expression and antibiotic production." Presented at: Perlman Antibiotic Discovery and Development Symposium; Madison, WI; Apr 27, 2018.}
{11}

\cvpub
{\underline{R Zarnowski}, \textbf{MG Chevrette}, E Dominguez, DR Andes. ``Modeling high-throughput proteomics into predictive metabolomics - A novel tool for studies of medical device-associated \textit{Candida spp.} biofilm infections." Presented at: Metabolomics Circle 2017 - Bioanylytical \& Omics Science, Wrocław, Poland; Nov 18, 2017.}
{12}

\cvpub
{\underline{D Acharya}, N Adnani, D Braun, IJ Miller, Q Yu, \textbf{MG Chevrette}, M Berres, CR Currie, L Li, JC Kwan, TS Bugni. ``Chemical cross-talk in bacterial co-cultures affects differential gene expression and antibiotic production." Presented at: American Society for Pharmacognosy Annual Meeting, Portland, OR; Jul 30, 2017.}
{13}

\cvpub
{AF Sanchez-Larrayoz, NM Elhosseiny, \textbf{MG Chevrette}, Y Fu, P Giunta, G Spallanzani, GB Pier, S Lory, \underline{T Maira-Litr\'{a}n}. ``The membrane lipid asymmetry transport system plays a key role in protecting \textit{Acinetobacter baumannii} against killing by human complement via the alternative pathway." Presented at: American Society for Microbiology Microbe, New Orleans, LA; Jun 2, 2017.}
{14}

\cvpub
{\underline{\textbf{MG Chevrette}}, CM Carlson, C Thomas, TS Bugni, DR Andes, CR Currie. ``Evolutionary trends in secondary metabolism reveal insect-associated \textit{Streptomyces} as an underexploited antibiotic resource." Presented at: Perlman Antibiotic Discovery and Development Symposium; Madison, WI; Mar 31, 2017.}
{15}

\cvpub
{\underline{EJ Caldera}, \textbf{MG Chevrette}, CR Currie. ``The geographic mosaic of antibiotic coevolution in a bacterial symbiont of the fungus-farming ant \textit{Apterostigma dentigerum}." Presented at: Perlman Antibiotic Discovery and Development Symposium; Madison, WI; Mar 31, 2017.}
{16}

\cvpub
{\underline{J Bratburd}, C Keller, E Vivas, \textbf{MG Chevrette}, F Rey, L Li, CR Currie. ``The human gut microbiota metabolomic response to infection." Presented at: Perlman Antibiotic Discovery and Development Symposium; Madison, WI; Mar 31, 2017.}
{17}

%\cvpub
%{\textbf{\underline{MG Chevrette}}, CR Currie, MH Medema.  ``prediCAT: An accurate predictive method for substrate specificity of nonribosomal peptide synthetase adenylation domains." Presented at: Kenneth B. Raper Symposium on Microbial Research; Madison, WI; Sep 2, 2016.}
%{18}
%
%\cvpub
%{\underline{J Bratburd}, BR McDonald, \textbf{MG Chevrette}, JL Klassen, HA Horn, CR Currie. ``Comparative genomics of fungus-growing ant-associated \textit{Pseudonocardia}." Presented at: Kenneth B. Raper Symposium on Microbial Research; Madison, WI; Sep 2, 2016.}
%{19}
%
%\cvpub
%{\underline{HA Horn}, E Gemperline, \textbf{MG Chevrette}, BR Mcdonald, J Bratburd, E Mevers, J Clardy, L Li, CR Currie. ``Mass spectrometry imaging reveals differential chemical response to pathogens in an ancient ant-microbe symbiosis." Presented at: ISME International Symposium on Microbial Ecology; Montreal, QC, Canada; Aug 21-26, 2016.}
%{20}
%
%\cvpub
%{\textbf{\underline{MG Chevrette}}, CR Currie, MH Medema.  ``Computational predictions of substrate specificity in nonribosomal peptide synthetases through comparative adenylation domain trees." Presented at: American Society for Microbiology Microbe; Boston, MA; Jun 16-20, 2016.}
%{21}
%
%\cvpub
%{\underline{SS Johnson}, ML Soni, DJ Collins, KC Benison, MR Mormile, \textbf{MG Chevrette}, BL Ehlmann. ``Biosignatures in mars analog acid salt lakes." Presented at: USRA Biosignature, Preservation and Detection in Mars Analog Environments; Lake Tahoe, Nevada; May 16-19, 2016.}
%{22}
%
%\cvpub
%{\textbf{\underline{MG Chevrette}}, C Carlson, C Thomas, TS Bugni, CR Currie. ``Multifaceted antibiotic profiling across Actinomycete chemical ecology." Presented at: Perlman Antibiotic Discovery and Development Symposium; Madison, WI; Apr 29, 2016.}
%{23}
%
%\cvpub
%{\underline{N Adnani}, S Adibhatla, E Vazquez-Rivera, GA Ellis, D Braun, \textbf{MG Chevrette}, BR McDonald, C Thompson, JS Piotrowski, Q Yu, L Li, CR Currie, TS Bugni. ``Driving production of novel natural products through marine microbial interspecies interactions." Presented at: Gordon Marine Natural Products; Ventura, CA; Mar 6-11, 2016.}
%{24}
%
%\cvpub
%{\textbf{\underline{MG Chevrette}}, DW Udwary, CR Currie, SS Johnson. ``Functional classification and secondary metabolism of an extreme metagenome." Presented at: Kenneth B. Raper Symposium on Microbial Research; Madison, WI; Sep 1, 2015.}
%{25}
%
%\cvpub
%{\textbf{\underline{MG Chevrette}}, BL Ehlmann, KC Benison, SS Johnson. ``Microbial diversity and biosynthetic potential of an extreme sediment metagenome." Presented at: Gordon Applied and Environmental Microbiology; South Hadley, MA; Jul 12-17, 2015.}
%{26}
%
%\cvpub
%{\textbf{\underline{MG Chevrette}}, M Vinacur, T Maira-Litr\'{a}n. ``Transposon-directed insertion site sequencing reveals \textit{in vivo} fitness factors in \textit{Acinetobacter baumannii} lung infections." Presented at: Boston Bacterial Meeting; Cambridge, MA; Jun 18-19, 2015.}
%{27}
%
%\cvpub
%{\underline{DW Udwary}, K Robison, \textbf{MG Chevrette}, GL Verdine. ``Lessons from long read assembly of 100+ Actinomycete genomes." Presented at: Gordon Marine Natural Products; Ventura, CA; Mar 2-7, 2014.}
%{28}
%
%\cvpub
%{\underline{K Robison}, DW Udwary, \textbf{MG Chevrette}, GL Verdine. ``Long read assembly of >100 Actinomycete genomes." Presented at: Advances in Genome Biology \& Technology; Marco Island, FL; Feb 12-15, 2014.}
%{29}
%
%\cvpub
%{\underline{S Young}, S Steelman, R Daza, \textbf{MG Chevrette}, R Lintner, S Gnerre, A Berlin, B Walker, C Nusbaum, R Nicol. ``Generation of high-quality draft assemblies with a single sequencing library." Presented at: Sequencing, Finishing, Analysis in the Future; Santa Fe, NM; May 29-31, 2013.}
%{30}
%
%\cvpub
%{\underline{S Steelman}, R Daza, \textbf{MG Chevrette}, P Kompella, P Trang, T Surabian, R Lintner, CZ Zhang, J Jung, M Meyerson, C Nusbaum, R Nicol. ``Automated low input mate-pair library construction for Illumina sequencing." Presented at: Advances in Genome Biology \& Technology; Marco Island, FL; Feb 15-18, 2012.}
%{31}
%
%\cvpub
%{S Steelman, R Daza, \underline{\textbf{MG Chevrette}}, P Kompella, P Trang, T Surabian, R Lintner, R Nicol. ``Microbial mate-pair library construction for de novo detection of structural rearrangements." Presented at: Broad Institute Symposium; Boston, MA; Nov 7-8, 2011.}
%{32}
%
\end{cvpubs}